Modeling Mortality Trends in Alberta

### 2024-03-15 outputs/paper/paper.qmd
intro updated
abstract added

---
title: "Modeling Mortality Trends in Alberta"
subtitle: "A Quantitative Approach to Public Health Dynamics"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/Alberta_Mortality_Rate.git"
date: today
date-format: long
abstract: "Abstract"
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Modeling Mortality Trends in Alberta"
subtitle: "A Quantitative Approach to Public Health Dynamics"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/Alberta_Mortality_Rate.git"
date: today
date-format: long
abstract: "This study is focusing on the mortality trends in Alberta, with an emphasis on understanding the broader public health implications. This study offers a panoramic view of the health challenges and demographic shifts influencing the mortality rates in the province. The findings highlight an increase in mortality over recent years, with implications that extend beyond individual health conditions to encompass wider societal and environmental factors. The paper underscores the importance of data-driven approaches in shaping effective public health strategies and policies."
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---
